Monitoring misinformation related interventions by Facebook, Twitter and YouTube: methods and illustration.

### 2021-08-30 article/draft.tex
rewrite conclusion for YT remove section

[CONCLUSION]
This drop in views can show that the  suspension  period may  have  a  good impact on reducing  the  audience interest or reach to the channel.

>>>>

As most YouTube channels upload videos on a weekly or even a monthly basis, a one-week suspension appears not very restrictive at first sight. 
But we observed that the intervention was followed by a reduction in the number of view for the two channels investigated, with one channel even stopping its YouTube activity in the following months. 
Although more research is needed before drawing a definitive conclusion, it is possible that the one-week suspension following a strike might reduce the reach of the very active YouTube channels.
